### 2020-06-11 writeup/proofs_sec3.tex
sec AB

Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
Now we can define the multi-task learning estimator for the target task as
	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task". 
%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
\begin{align}
	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
\end{align}
which is well-defined since it only depends on $\hat v$, but otherwise does not depend on $\hat w_1$ or $\hat w_2$ separately.

\textbf{Extended related work.}
McNamara and Balcan \cite{NB17}

Bullins et al. \cite{BHKL19}

Cavallanti et al. \cite{CCG10}

Daume and Marcu \cite{DM06}

Zhao et al. \cite{ZD19}

>>>>

Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
Now we can define the multi-task learning estimator for the target task as
	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task". 
%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
\begin{align}
	\te(\hat{\beta}_2^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
\end{align}
which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.

\textbf{Extended related work.}
Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
For such models, their output dimension plays an important role of regularization \cite{KD12}.
Linear models in the context of multi-task learning have been studied in various settings, including representation learning \cite{BHKL19}, online learning \cite{CCG10,DCSP18}, and sparse regression \cite{LPVT11}.

### 2020-06-11 writeup/related.tex
sec AB

\textit{Multi-task learning theory.}
Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors in an optimal way.
The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
Our work is closely related to Wu et al. \cite{WZR20}.
While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques do not explain the phenomena of negative transfer.

>>>>

\textit{Multi-task learning theory.}
Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors in an optimal way.
The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
Our work is closely related to Wu et al. \cite{WZR20}.
While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
